% !TeX TXS-program:bibliography = txs:///biber
%%% -*- latex -*- 
%%%
%%% cv-vilhuber.tex
%%% Time-stamp: <11/07/04 08:11:42 vilhuber>
%%% $Id: cv-vilhuber.tex 2918 2018-03-03 21:58:22Z lv39 $
%%% $URL: https://forge.cornell.edu/svn/repos/proposals/general/cv-vilhuber.tex $
%%%
\documentclass[12pt,letterpaper]{article}
\newcommand{\mytitle}{Lars Vilhuber}
\newcommand{\myversion}{\today}

% Choose Times New Roman

\usepackage{mathptmx}
\usepackage[T1]{fontenc}

%\usepackage{pstricks}
%\usepackage{color}
\usepackage[usenames]{xcolor}
\usepackage{fancyhdr}   % provides pagestyle fancy
\definecolor{myred}{rgb}{1 .1 0}
\definecolor{myblue}{rgb}{0,.1,1}
\definecolor{cornellred}{rgb}{0.7,.11,.11}
\usepackage{fullpage}
\usepackage{hyperref}
\hypersetup{ %
	plainpages,%
	colorlinks,%
	linkcolor=cornellred,
	urlcolor=cornellred,
	filecolor=blue,
	citecolor=blue,
	breaklinks,
	pdftitle={\mytitle},%
	pdfpagemode=None,%UseOutlines
	pdfauthor={\mytitle},%
	pdfsubject={Research Contributions and Relevant Experience}%
}
%\usepackage{newcent}
\usepackage{longtable}
%\usepackage{t1enc}
\pagestyle{fancy}

\usepackage[inline]{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}

\usepackage{titlesec}
\titlespacing*{\section}{0pt}{6pt}{6pt}
\titlespacing*{\subsection}{0pt}{0pt}{0pt}
\titlespacing*{\paragraph}{0pt}{0pt}{0pt}
\titleformat*{\section}{\Large\bfseries}
\titleformat*{\subsection}{\large\bfseries}


% % % % % % % % BIBLATEX
\usepackage{csquotes}
\usepackage[backend=biber,sortcites,sorting=ydnt,maxbibnames=20,style=apa]{biblatex}
\addbibresource{abbrev.bib}
\addbibresource{self.bib}
\addbibresource{data.bib}

\DeclareBibliographyCategory{dataset}
\addtocategory{dataset}{AbowdVilhuber_NQWIDATA}
\addtocategory{dataset}{lange_fabian_2020_3966534}
\addtocategory{dataset}{foote_andrew_d_2020_4072428}

% Clear some stuff from the bibliography
\AtEveryBibitem{%
  \clearfield{note}%
	\clearfield{day}%
	\clearfield{month}%
	\clearfield{endday}%
	\clearfield{endmonth}%
	\clearlist{language}%
	\clearfield{issn}%
	\clearfield{eprint}% - adjust if necessary
	\iffieldundef{doi}{}{\clearfield{url}}% remove URL field if DOI present    
}

%\addbibresource[location=remote]{http://www.vilhuber.com/lars/wp-content/papercite-data/bib/self.bib}
\defbibfilter{collective}{
	type=incollection or
	type=inproceedings
}

\defbibfilter{books}{
	type=book or
	type=inbook
}

% % % % % % % % Layout
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\setlength{\headsep}{18pt}
\newcommand{\otherpages}{%
\fancyhead[LO,RE]{{\small \it  Research Contributions and Relevant Experience}}
\fancyhead[RO,LE]{{\small \it \mytitle}}
\fancyfoot[RO,LE]{Page \thepage }
\fancyfoot[CO,CE]{\ \ }
%\fancyfoot[RO,LE]
%{\tiny Latest version at \href{http://www.cloutier-vilhuber.net/Lars/cv-vilhuber.pdf}{http://www.cloutier-vilhuber.net/Lars/cv-vilhuber.pdf}}
}
\otherpages
%\pagestyle{myheadings}
%\markboth{\myversion}{\mytitle}

%\thispagestyle{empty} 
\begin{document}
\thispagestyle{empty}

\section{Research Contributions Over the Last Six Years}

\subsection*{Refeered contributions}

\paragraph{Journal articles:}
\fullcitebib{FooteKutzbachVilhuber2021,vilhuber.metajelo.2021,alam2020,McKinneyEtAl:accepted:2017,Vilhuber2020Reproducibility,ncrn-summary}

\paragraph{Refereed books and book chapters:} 
\fullcitebib{NAP25303,NAP25305,NAP25639,NAP25707}

\newpage 

\subsection*{Other refereed contributions}

%Examples include papers presented at scholarly meetings or conferences, articles in professional or trade journals, etc.

\fullcitebib{AEAPP2019,PistnerSlavkovicVilhuber:PSD:2018,HaneySIGMOD2017,chance:2017}

\subsection*{Non-refereed contributions}

%Examples include book reviews, published reviews of your work, research reports, policy papers, public lectures, etc.
\fullcitebib{templateREADME,%
%
%\paragraph{Editorials and published annual reports:}
%\fullcitebib{%
Dwork_Karr_Nissim_Vilhuber_2021,Vilhuber_2021,ReportDE2021,ReportDE2020,ReportDE2019,Vilhuber2018,Slavkovic2018,%
%}
%\paragraph{Books and book chapters}
%
%\fullcitebib{
cole2020,ShenVilhuber2020,SchmutteVilhuber2020,%
%
%\paragraph{Data and Code}
%
%\fullcitebib{%
alam2020applying,foote_andrew_d_2020_4072428,lange_fabian_2020_3966534}


\subsection*{Forthcoming contributions}

%Indicate one of the following statuses—"submitted", "revised and submitted", "accepted" or "in press". Contributions not yet submitted should not be listed. Provide the name of the journal or book publisher and the number of pages. 
\begin{itemize}
  \item ``Reproducibility and Transparency versus Privacy and Confidentiality: Reflections from a Data Editor'', \textit{Journal of Econometrics}, submitted.
  \item ``Teaching for large-scale Reproducibility Verification'', \textit{Journal of Statistics and Data Science Education}, revised and submitted.
\end{itemize}

\section{Other Research Contributions}

% Describe any other contributions to research and the advancement of knowledge within the last six years, including your research contributions to non-academic audiences (e.g., general public, policy-makers, private sector or not-for-profit organizations, etc.).

\paragraph{Editorial activities:\ }
 Managing Editor of the Journal of Privacy and Confidentiality, 2017-,
 Data Editor for the American Economic Association, 2018-,
Guest Editor for special issue on Linked Employer-Employee Data, Journal of Econometrics, 2019-2021,
	 Associate Editor of the Harvard Data Science Review, 2019-

\paragraph{Committees and Panels:\ } 
Committee on the Future of Scholarly Communications (Cornell University), member 2019-2022; 
Contribution to activities of the (U.S.) National Academies of Science, Engineering, and Medicine:
\begin{itemize*}
	\item \href{https://www8.nationalacademies.org/pa/projectview.aspx?key=51436}{Forecasting Costs for Preserving, Archiving, and Promoting Access to Biomedical Data} 
	\item \href{https://www8.nationalacademies.org/pa/projectview.aspx?key=51187}{Transparency and Reproducibility of Federal Statistics for the National Center for Science and Engineering Statistics} 
	\item  Presentation at ``\href{https://www8.nationalacademies.org/pa/projectview.aspx?key=49809}{Workshop on Transparency and Reproducibility in Federal Statistics}''
	\item Presentation to ``\href{https://www8.nationalacademies.org/pa/projectview.aspx?key=49906}{Committee on Reproducibility and Replicability in Science}''
\end{itemize*} 
%
Member of the Board of Directors of the \href{https://crdcn.org/}{Canadian Research Data Centre Network}/ R\'eseau canadien des Centres de donn\'ees de recherche, 2019- ;
American Statistical Association, \href{http://community.amstat.org/cpc/home}{Committee on Privacy and Confidentiality}, member 2016-2021, chair 2021; 
Comit\'e scientifique du \href{https://casd.eu/}{Centre d'acc\`es s\'ecuris\'e aux 
donn\'ees} (CASD) [Scientific advisory board of the Center for secure data 
access, France], member 2012-2014, chair 2014-;
Conseil d'orientation du \href{https://ciqss.org}{Centre interuniversitaire 	qu\'eb\'ecois de statistiques sociales} (CIQSS)/ Advisory board of the Quebec Inter-University 
Centre for Social Statistics (QICSS) [Canada], member, 2014-;
Social Sciences and Humanities Research Council of Canada (SSHRC), Adjudication Committee for Partnership Grants, member 2018-2019;
National Science Foundation, Methodology, Measurement, and Statistics (MMS) Advisory Panel, member 2016-2018;

\section{Most Significant Career Research Contributions}

\begin{enumerate}
\item \fullcite{templateREADME}\newline The template README has already been used by several hundred manuscripts, and greatly improved reproducibility of journal articles.
\item \fullcite{Ashwin2008}\newline
Documents the first large-scale implementation of differential privacy, an innovative and greatly superior way of publishing data while preserving respondents privacy. 
\item \fullcite{AbowdEtAl2009}\newline
Documents the publication of a novel data resource, still being produced by the U.S. Census Bureau, with 1,000s of downloads, and use far beyond academia. Innovative in its use of disclosure avoidance to provide detailed tabular statistics at unprecedented levels.
\item \fullcite{AbowdVilhuber2008}\newline
One of the earliest publications identifying the privacy protective power of synthetic (artificial data).
\item \fullcite{AbowdVilhuber2005}\newline
Often cited to illustrate that administrative data is not perfect, and can be biased for reasons (at the time) not well appreciated by the economics and statistics communities.
\end{enumerate}

\section{Career Interruptions and Special Circumstances}

None.

\section{Contributions to Training}

\paragraph{Graduate thesis committees:\ }

Ph.D. Committee member for: Raghunathan, Kalyani (2015)
Green, Andrew	(2017).
%
M.Sc. Committee member for: Daniel Li (2019)

\paragraph{Undergraduate involvement in research: }

Since 2015, I have involved about 90 students in research projects that I am involved with. The bulk of these have been trained and employed as part of the LDI Replication Lab, verifying reproducibility for the American Economic Association.


\newpage


\section{Relevant Experience}

As Data Editor for the American Economic Association, I have organized the LDI Replication Lab. Each semester, including the summer semester, we train 12-15 students in methods to verify data provenance and reproducibility. Over 75 students have been trained so far, and at any point in time, about 15-25 students are active in the lab. Over 1,000 articles have been evaluated since the Lab opened. 

I have also organized several conferences, including being lead organizer on the ``Conference on Models of Linked Employer-Employee Data'' (with Sloan and Cornell funding). A conference volume, to be published by the Journal of Econometrics, is currently being finalized. 

As lead PI for the second half of the NSF-funded ``RCN: Coordination of the NSF-Census Research Network'' project, we organized two workshops per year, with presentations from researchers working on eight different NSF-funded projects. Working papers by the network were archived (preserved), and the entire research coordination website was preserved at the end of the grant. An NSF-organized mid-term evaluation deemed the work of the Coordination Office to be fully satisfactory. A summary publication of the network's work was published by the \textit{Journal of Survey Statistics and Methodology} (Weinberg et al, 2018), and the network was awarded a prize by the American Statistical Association for excellent networking between academia and government.

\end{document}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% TeX-master: t
%%% End: 
